%-------------------------
% ATS-Optimized Resume in LaTeX
% Madeti Pavan Kumar | IoT & Embedded Systems Engineer
% Compile with: pdflatex or xelatex
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins -- 0.5in all sides
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%--------- CUSTOM COMMANDS ---------

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-1pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, itemsep=0pt, parsep=0pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%===================================================
%              RESUME STARTS HERE
%===================================================

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Madeti Pavan Kumar} \\ \vspace{4.5pt}
    \small
    Vizianagaram, Andhra Pradesh \textbar{}
    \faPhone\ 6302085024 \textbar{}
    \href{mailto:madetipavankumar9@gmail.com}{\faEnvelope\ \underline{madetipavankumar9@gmail.com}} \textbar{}
    \href{https://linkedin.com/in/pavankumarmadeti}{\faLinkedin\ \underline{linkedin.com/in/pavankumarmadeti}} \textbar{} 
    \href{https://github.com/Pavan-1522}{\faGithub\ \underline{github.com/Pavan-1522}}
\end{center}

\vspace{-6pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\resumeSubHeadingListStart
\item\small{
Dynamic \textbf{IoT \& Embedded Systems Engineer} with hands-on expertise delivering \textbf{50+ commercial automation projects}. Skilled in rapid prototyping, PCB design, and cloud integration, with a growing focus on automotive-grade systems (\textbf{QNX RTOS}, \textbf{CAN Bus}) to solve real-world problems at scale.
}
\resumeSubHeadingListEnd

\vspace{-6pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {GMR Institute of Technology (GMRIT)}{Expected May 2027}
    {Bachelor of Technology (B.Tech) -- Electronics and Communication Engineering (ECE)}{Rajam, Andhra Pradesh}

  \resumeSubheading
    {Chaitanya Engineering College}{2021 -- 2024}
    {Diploma in Electronics and Communication Engineering (ECE)}{Visakhapatnam (Kommadi), Andhra Pradesh}

\resumeSubHeadingListEnd

\vspace{-6pt}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Freelance IoT \& Embedded Systems Developer}{2023 -- Present}
    {Independent Consultant -- Hardware \& Firmware Engineering}{Remote / Andhra Pradesh}
  \resumeItemListStart
    \resumeItem{Designed and delivered \textbf{50+ end-to-end custom IoT hardware projects} spanning home automation, smart agriculture, and vehicle tracking, managing the full lifecycle from schematic design to PCB fabrication and firmware development.}
    \resumeItem{Generated \textbf{{\rupee}1,00,000+ in revenue} by successfully commercializing embedded solutions and consulting for engineering clients.}
  \resumeItemListEnd

  \resumeSubheading
    {RoboCoupler Pvt. Ltd.}{May 2025 -- Present}
    {Intern -- PCB Design \& IoT Hardware Development}{Visakhapatnam, Andhra Pradesh}
  \resumeItemListStart
    \resumeItem{Spearheaded design of the \textbf{KIWI Board} -- a custom IoT development board integrating ESP8266, L298N motor driver, and multi-sensor interfaces -- from schematic capture to DFM-ready PCB layout.}
    \resumeItem{Executed complete PCB design lifecycle using KiCad/Eagle, including component selection, routing, and design rule checks (DRC) to ensure manufacturability.}
    \resumeItem{Prototyped, debugged, and validated custom IoT firmware, accelerating product development cycles.}
  \resumeItemListEnd

  \resumeSubheading
    {CEMS -- Centre of Excellence in Maritime and Shipbuilding}{June 2025}
    {Intern -- IIoT and Microcontroller Systems}{Visakhapatnam, Andhra Pradesh}
  \resumeItemListStart
    \resumeItem{Integrated industrial sensors with \textbf{ESP32/ESP8266} microcontrollers and IIoT platforms (Node-RED, Blynk) to build proof-of-concept remote monitoring and automation prototypes.}
    \resumeItem{Developed and deployed multiple IIoT prototypes simulating real-world industrial automation scenarios for maritime applications.}
  \resumeItemListEnd

  \resumeSubheading
    {Resolute Sky Quad Electronics}{June 2023 -- Nov 2023}
    {Production Intern -- PCB Assembly \& Quality Assurance}{Medchal, Hyderabad}
  \resumeItemListStart
    \resumeItem{Performed SMT component placement, fine-pitch soldering, and QA testing for \textbf{Fire-Boltt smartwatches}, maintaining strict ESD protocols to measurably reduce manufacturing defect rates.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6pt}

%-----------KEY PROJECTS-----------
\section{Key Projects}

\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Smart Bus Pass Verification System (APSRTC)} $|$ \emph{ESP32, RFID, Firebase, JavaScript} $|$ \textbf{\color{black}[\faFileAlt~Patent Filed]}}{2024 -- Present}
  \resumeItemListStart
    \resumeItem{\textbf{Situation:} Manual bus pass verification at APSRTC checkpoints was slow, error-prone, and offered no real-time transaction visibility.}
    \resumeItem{\textbf{Task/Action:} Engineered a fully automated RFID-based verification system using ESP32, with real-time balance display on an onboard LCD and a live data pipeline to Firebase Realtime Database and Google Sheets.}
    \resumeItem{\textbf{Result:} Eliminated manual processing delays; system showcased at \textbf{multiple technical symposiums}, winning \textbf{multiple 1st-place prizes} for innovation. \textbf{Patent application filed} for the core system architecture.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Predictive Cold Chain Monitoring System} $|$ \emph{ESP32, GPS, MQTT, Blockchain, Python}}{2024}
  \resumeItemListStart
    \resumeItem{Developed an advanced IIoT system for monitoring critical medical supplies in transit, tracking \textbf{real-time temperature, humidity, vibration, and GPS coordinates} via a live hospital-facing dashboard.}
    \resumeItem{Implemented \textbf{predictive maintenance algorithms} to forecast AC cooling unit failures by analyzing power consumption metrics, enabling proactive intervention before spoilage occurs.}
    \resumeItem{Architected a \textbf{blockchain-secured data layer} to store immutable transit records, providing verified, tamper-proof medicine status to receiving hospitals and ensuring supply chain transparency.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Automated UPI Pad Dispensing System} $|$ \emph{ESP32, UPI Payment API, Servo/Stepper Motor}}{2024}
  \resumeItemListStart
    \resumeItem{Engineered a smart, unattended sanitary pad dispenser integrated with \textbf{UPI mobile payment} infrastructure for fully automated, cashless dispensing -- improving accessibility in public and institutional spaces.}
    \resumeItem{Designed the embedded firmware to validate UPI payment confirmation callbacks and trigger the mechanical dispensing mechanism in real time.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Smart Home Automation via Cloud} $|$ \emph{ESP32, Firebase, HTML, JavaScript}}{2023}
  \resumeItemListStart
    \resumeItem{Built a scalable cloud-connected home automation platform enabling remote appliance control and real-time status monitoring through a custom web interface backed by Firebase Realtime Database.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

% ---- Other Notable Projects ----
\vspace{-8pt}
\textbf{\small Other Notable Projects:} \small Smart Energy Meter (IoT power analytics), Smart Farm Monitoring Robot (autonomous field robot), Vehicle Monitoring System (GPS + OBD telematics), Smart Toll Gate System (RFID automated toll). \textit{50+ total projects delivered.}

\vspace{-2pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\item \small{
  \textbf{Core Competencies:} IoT System Design, Embedded Systems, Industrial Automation, Predictive Maintenance, RFID/NFC Integration, PCB Design, Rapid Hardware Prototyping, Blockchain Data Security \\[2pt]
  \textbf{Microcontrollers \& SBCs:} ESP32, ESP8266, Arduino (Uno/Nano/Mega), STM32, Raspberry Pi, AT89S52, PIC16F877A \\[2pt]
  \textbf{Protocols \& RTOS:} MQTT, Modbus, CAN Bus, HTTP/REST, I2C, SPI, UART, QNX RTOS \textit{(in progress)} \\[2pt]
  \textbf{Cloud \& IoT Platforms:} Firebase Realtime Database, Google Sheets API, Blynk, ThingSpeak, Node-RED \\[2pt]
  \textbf{Languages \& Tools:} C, Embedded C, Python, JavaScript, HTML/CSS, Java \\[2pt]
  \textbf{Hardware \& EDA Tools:} KiCad, Eagle, Arduino IDE, VS Code, SMT Soldering, Oscilloscope, Signal Analyzer \\[2pt]
  \textbf{OS \& Platforms:} Linux (Ubuntu), GitHub, Node-RED
}
\resumeSubHeadingListEnd

\vspace{-6pt}

%-----------LEADERSHIP & ACHIEVEMENTS-----------
\section{Leadership \& Achievements}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, parsep=0pt, topsep=2pt]
  \resumeItem{\textbf{Club Coordinator} (ISTE \& Robotics Club, GMRIT): Managed \textbf{10+ volunteers}, mentored \textbf{15+ juniors} in hardware design, and organized \textbf{5+ technical workshops} reaching over \textbf{200 students} (2023 -- Present).}
  \resumeItem{\textbf{Patent Filed:} Core system architecture for the Smart Bus Pass Verification System (APSRTC).}
  \resumeItem{\textbf{1st Prize ({\rupee}10,000 Award):} STEPCONE 2025, GMRIT National Level Tech Fest (out of 50+ teams).}
  \resumeItem{\textbf{1st Prize Wins:} JNTUK Robotics Workshop \& Chaitanya Engineering College Technical Events.}
\end{itemize}

\end{document}